%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Haiyang Yu } & \href{mailto:haiyangy@andrew.cmu.edu}{haiyangy@andrew.cmu.edu}\\
  \href{https://www.linkedin.com/in/haiyang-yu-246a213b/}{https://www.linkedin.com/in/haiyang-yu-246a213b/} & +1-408-839-3245 \\ 
  & Cupertino, CA \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carnegie Mellon University Silicon Valley}{Mountain View}
      {Master of Science in Software Engineering}{Jan. 2018 -- May. 2019}
    \resumeSubheading
      {Nanyang Technological University}{Singapore}
      {Bachelor of Engineering, Electrical and Electronic Engineering;  GPA: 4.61/5.0}{Aug. 2010 -- May. 2014}
    \vspace{-2pt}
    \item{
      \textbf{Courses}{: Foundations of Computer Systems, Data Structure and Algorithm, Practical Data Science, Foundations of Software Engineering}
    }
  \resumeSubHeadingListEnd

%--------TECHNICAL SKILLS------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Java, Python, C, Shell, HTML, JavaScript, SQL}
    }
    \item{
      \textbf{Technologies}{: Android, Angular, Angular Material, Ceph, Consul, Docker, Docker Compose, Express.js, Gradle, gRPC, Google Guava, HOCON, Linux, MapReduce, MongoDB, Node.js, NumPy, Pandas, Registrator}
    }
  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Moqi.ai (Java, Shell)}{Beijing, China}
      {Software Engineer Intern}{May 2018 - Aug 2018}
      
      \vspace{2pt}
      
      \small{Designed and implemented fingerprint system fault tolerance that improved system uptime from 93\% to 99\%}
      
      \vspace{-8pt}
            
      \resumeItemListStart
      
        \resumeItem{Ceph Filesystem}
          {Set up \textbf{Ceph Filesystem} with \textbf{Erasure Coding} as main distributed storage for segments cached in matching servers' memory.}
      
        \resumeItem{Fingerprint System Docker Compose}
          {Simplified fingerprint system testing through creating \textbf{docker compose} file to run the entire fingerprint system on a single server. The fingerprint system consists of heterogeneous \textbf{gRPC} services written in Java, Python, C++ as well as Redis, Cassandra and SeaweedFS.}
          
        \resumeItem{Matching Server Fault Tolerance}
          {Designed and implemented auto discovery of online/offline \textbf{dockerized} matching servers through \textbf{Consul} and \textbf{Registrator}, which triggers segment redistribution among matching servers and segment recovery from Ceph Filesystem.}
          
        \resumeItem{Controller Fault Tolerance}
          {Designed and implemented Controller \textbf{Active/Standby Failover} through \textbf{Consul's Leader Election}.}
        
      \resumeItemListEnd
      
    \resumeSubheading
      {Barclays Capital Services (Java)}{Singapore}
      {Software Engineer}{Jun 2014 - Dec 2017}
      \resumeItemListStart
        \resumeItem{Trade Reporting Processor}
          {Developed Trade Reporting Processor that retrieves and applies trade reporting obligations. Implemented caching of index constituents using \textbf{Google Guava} that cut down query time by 50\%.}
          
        \resumeItem{Market Object and Static Services}
          {Developed a greenfield market data calculation application which used \textbf{Redis} for caching, \textbf{Elasticsearch} for logging and \textbf{Akka} for concurrency.}
          
        \resumeItem{Sparta Automatic Deployment}
          {Fully automated Sparta deployment to 24 servers across 5 countries that used to be manual and sluggish. This consisted of migrating Sparta from \textbf{Perforce} to \textbf{Git} version control system, and implementing continuous deployment through \textbf{TeamCity} and \textbf{Nolio}.}

      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  
    \resumeSubItem{Malloc (C)}
      {Independently implemented a \textbf{dynamic memory allocator} using \textbf{segregated free list} that achieved 74.1\% memory utilization and 20,000 throughput.}
      
      \resumeSubItem{Movie Box Office Prediction (Python)}
      {Crawled raw html of over 8,000 movies from Box Office Mojo and parsed them into meaningful data using \textbf{lxml}. Processed 30 million pieces of movie information using \textbf{MapReduce}. Extracted features using \textbf{Pandas}, \textbf{NumPy} and \textbf{One Hot Encoding}. Trained 2 prediction models using \textbf{Linear Regression} and \textbf{Decision Tree Regression}. Compared their accuracy based on \textbf{mean squared error}.}

    \resumeSubItem{Emergency Social Network (Angular, Node.js, MongoDB)}
      {Developed a chat application designed for times of disaster that provides functions including public chat, private chat, post announcement, share status, user administration and emergency contacts. Used \textbf{Angular} and \textbf{Angular Material} for frontend, \textbf{Express.js} and \textbf{Node.js} for backend, \textbf{MongoDB} for database.}
    
    \resumeSubItem{Face Fengshui App (Android)}
      {Independently developed an \textbf{Android} application that performs face recognition on a person’s selfie to predict his/her fortune and temperament based on face reading techniques.}

  \resumeSubHeadingListEnd

\end{document}